Analysis paper

### 2021-06-03 analysis/analysis.Rmd
update plots

df <- eval_forecasts(
  filtered_data[model %in% regular_models], 
  summarise_by = c("model", "horizon", "target_type")
)

df <- df %>%
  merge(df[model == "Hub-ensemble", 
           .(horizon, target_type, base_score = interval_score)])
df[, rel_score := (interval_score / base_score) * 100 - 100]
df[, diff_score := interval_score - base_score]
df[, .(horizon, target_type, model, rel_score, diff_score)][order(target_type, horizon)]

@@

@@

distribution_plot <- function(df, x = "scaled_rel_skill") {
  df %>%
  ggplot(aes_string(y = "model", x = x, 
                          group = "model", fill = "model")) + 
  ggridges::geom_density_ridges(quantile_lines = TRUE, quantiles = 0.5) + 
  geom_vline(aes(xintercept = 1), alpha = 0.4) + 
  scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[2:5]) + 
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  theme(legend.position = "bottom") + 
  labs(y = "Scaled relative skill") + 
  scale_x_log10(labels = scales::number_format(accuracy = 0.1), 
                limits = c(0.015, 50))
}

distribution_plot_wis <- function(df, x = "interval_score") {
  df %>%
  ggplot(aes_string(y = "model", x = x, 
                          group = "model", fill = "model")) + 
  ggridges::geom_density_ridges(quantile_lines = TRUE, quantiles = 0.5) + 
  scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
  theme(panel.background = element_rect(fill = "#e1f0fe")) +
  theme(legend.position = "bottom") + 
  labs(y = "Scaled relative skill") + 
  scale_x_log10(labels = scales::number_format(accuracy = 1))
}

@@

p_combined_wis <- distribution_plot_wis(df = scores, 
                                        x = "interval_score") +
  facet_wrap(~ target_type, ncol = 1, scales = "free_x")

@@

p_wis <- distribution_plot_wis(df = scores) + 
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(), 
        axis.ticks.y = element_blank()) + 
  facet_wrap(~ location_target, ncol = 2, scale = "free_x")

p_ae <- distribution_plot_wis(df = scores, x = "aem") + 
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(), 
        axis.ticks.y = element_blank()) + 
  facet_wrap(~ location_target, ncol = 2, scale = "free_x")

@@

pl
ggsave("plots/distribution_scores.png")

@@

pl_wis
ggsave("plots/distribution_scores_wis.png")

@@

pl_ae
ggsave("plots/distribution_scores_ae.png")

>>>>

df <- eval_forecasts(
  filtered_data[model %in% regular_models], 
  summarise_by = c("model", "horizon", "target_type"), 
  compute_relative_skill = TRUE, 
  baseline = "Hub-ensemble"
)

df <- df %>%
  merge(df[model == "Hub-ensemble", 
           .(horizon, target_type, base_score = interval_score)])
df[, rel_score := (interval_score / base_score) * 100 - 100]
df[, diff_score := interval_score - base_score]
df[, .(horizon, target_type, model, rel_score, scaled_rel_skill, diff_score)][order(target_type, horizon)]

@@

### Look at ensemble forecasts

```{r}

models_plot <- c("Crowd forecast", "Hub-ensemble-with-crowd", "Hub-ensemble")

comparison_ensembles <- function(models_to_plot) {
  df <- unfiltered_data[model %in% models_to_plot &
                          quantile %in% c(0.025, 0.25, 0.5, 0.75, 0.975)] %>%
    dcast(... ~ quantile, value.var = "prediction")
  df <- merge(
    df[, c("classification", "speed") := NULL], 
    copy(epitrend)[, forecast_date := NULL], 
    by = c("target_end_date", "location_name", "target_type")
  )

  p <- df[grepl(2, target)] %>%
    ggplot(aes(y = `0.5`, x = target_end_date, color = model)) +
    geom_line() + 
    theme_light() + 
    facet_wrap(~ location_target, scales = "free", ncol = 2) + 
    theme(legend.position = "bottom") + 
    theme(panel.background = element_rect(fill = "#e1f0fe")) + 
    scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 14, 
                            max(forecast_dates$full_hub_period)))

  return(p)
}

comparison_ensembles(models_plot)

@@

distribution_plot <- function(df, x = "scaled_rel_skill") {
  df %>%
    ggplot(aes_string(y = "model", x = x, 
                      group = "model")) + 
    geom_density_ridges(aes(fill = model), 
                                  quantile_lines = TRUE, quantiles = 0.5, 
                                  rel_min_height = 0.01) + 
    geom_vline(aes(xintercept = 1), alpha = 0.4) + 
    scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[2:5]) + 
    theme(panel.background = element_rect(fill = "#e1f0fe")) +
    theme(legend.position = "bottom") + 
    labs(y = "Scaled relative skill") + 
    scale_x_log10(labels = scales::number_format(accuracy = 0.1))
}

distribution_plot_wis <- function(df, x = "interval_score") {
  df %>%
    ggplot(aes_string(y = "model", x = x, 
                      group = "model", fill = "model")) + 
    geom_density_ridges(aes(fill = model), 
                        quantile_lines = TRUE, quantiles = 0.5, 
                        rel_min_height = 0.005, 
                        scale = 0.95, 
                        jittered_points = TRUE, 
                        position = position_points_jitter(width = 0.05, height = 0),
                        point_size = 1.5, 
                        point_shape = 21,
                        #point_shape = '|',
                        point_alpha = 1, 
                        alpha = 0.7) + 
    geom_density_ridges(quantile_lines=TRUE,
                        quantile_fun=function(x,...) mean(x), 
                        linetype = "dotted", 
                        alpha = 0, 
                        scale = 0.95, 
                        rel_min_height = 0.01) +
    scale_fill_manual(values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
    # scale_color_manual(aesthetics = "point_color", 
    #                    values = brewer.pal(name = "Accent", n = 5)[1:5]) + 
    theme(panel.background = element_rect(fill = "#e1f0fe")) +
    theme(legend.position = "bottom") + 
    labs(y = "Model", x = "Weighted interval score") + 
  scale_x_continuous(labels = scales::label_number(suffix = "k", 
                                                   scale = 1e-3, 
                                                   accuracy = NULL))
}

@@

p_combined_wis <- distribution_plot_wis(df = scores, 
                                        x = "interval_score") +
  facet_wrap(~ target_type, ncol = 1, scales = "free") + 
  theme(plot.margin=unit(c(0,0.4,0,0),"cm"))

@@

p_wis <- distribution_plot_wis(df = scores) + 
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(), 
        axis.ticks.y = element_blank()) + 
  facet_wrap(~ location_target, ncol = 2, scale = "free")

p_ae <- distribution_plot_wis(df = scores, x = "aem") + 
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(), 
        axis.ticks.y = element_blank()) + 
  facet_wrap(~ location_target, ncol = 2, scale = "free")

@@

ggsave("plots/distribution_scores.png", plot = pl, height = 9)

@@

ggsave("plots/distribution_scores_wis.png", pl_wis, height = 9)

@@

ggsave("plots/distribution_scores_ae.png", pl_ae, height = 9)
